ENME 625 \\ Multi-Objective Optimization with Genetic Algorithms

### 2017-05-10 draft1_SM.tex
merging changes
added more content

This report develops multi-objective optimization methods using genetic algorithms. Three cases of multi-objective optimization are considered: unconstrained optimization, constrained optimization, and robust optimization. A fitness function for the first two cases was developed using the built-in MATLAB 'ga' routine. The last case was developed such that uncertainty in function parameters could be handled and robustly optimized against. \newline

\noindent Each method developed was evaluated through the use of well-known test problems. The resulting Pareto frontier of each method was evaulated in terms of quality metrics. Finally, the results of the developed methods were compared to results obtained by using the built-in MATLAB 'gamultiobj' routine.

@@

\noindent The true Pareto frontier for this problem occurs when $x_i = 0$ for i = 2,...,30. Figure~\ref{fig:ZDT1} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. In this problem, $\alpha=1$, $\sigma = 0.158$, and $\epsilon = 0.22$. The final results were found using 300 chromosomes in each population. The quality metrics chosen to evaluate this problem (and all other problems) are Coverage Difference (CD) and Pareto Spread (OS). Ten runs for each algorithm were performed using the same initialization parameters and the mean and standard deviation of each metric are tabulated in Table~\ref{tab:ZDT1}.

\begin{figure}[h]
  \caption{Example Pareto Results for ZDT1}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT1_pareto_final.png}  
  \label{fig:ZDT1}
\end{figure}

\begin{table}[h]
\caption{Quality Metrics for ZDT1} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.3874 (0.0164) &  0.3582 (0.0040) \\ \hline
OS & 0.9605 (0.1088) & 0.9283 (0.0928) \\ \hline
\end{tabular}
\label{tab:ZDT1} 
\end{table}
\begin{figure}[h]
  \caption{ZDT1 Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT1_QM.png}  
  \label{fig:ZDT1_QM}
\end{figure}

@@

\begin{table}[H]
\caption{Quality Metrics for ZDT2} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.7832  (0.0821) & 0.6971  (0.0094) \\ \hline
OS &  0.8781 (0.0946) & 1.0086 (0.0278)  \\ \hline
\end{tabular}
\label{tab:ZDT2} 
\end{table}
\begin{figure}[H]
  \caption{ZDT2 Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT2_QM.png}  
  \label{fig:ZDT2_QM}
\end{figure}
\newpage
\newpage
\newpage
\goodbreak
\newpage

\goodbreak

\newpage
\goodbreak
\subsection{ZDT3} 
The third test problem, denoted as ZDT3 in \cite{deb2001multi} is shown below.

@@

\noindent The true Pareto frontier for this problem again occurs when $x_i$ = 0 for i = 2,...,30. The fitness parameters selected in this problem were $\alpa = 1$, $\sigma = 0158$ and $\epsilon = 0.22$. Again, the number of chromosomes in this problem was 300. Figure~\ref{fig:ZDT3} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:ZDT3} summarizes the mean quality metrics for each algorithm for ten runs. \newline

@@

\begin{table}[H]
\caption{Quality Metrics for ZDT3} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.7407 (0.0050) & 0.7554 (0.0031) \\ \hline
OS & 0.8565 (0.0098) & 0.8489 (0.0180) \\ \hline
\end{tabular}
\label{tab:ZDT3} 
\end{table}
\begin{figure}[h]
  \caption{ZDT3 Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT3_QM.png}  
  \label{fig:ZDT3_QM}
\end{figure}

@@

\noindent Figure~\ref{fig:OSY} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:OSY} summarizes the mean quality metrics for each algorithm for ten runs.
\begin{figure}[h]
  \caption{Example Pareto Results for OSY}
  \centering
  \includegraphics[width=0.85\textwidth]{OSY_pareto_final.png}  
  \label{fig:OSY}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for OSY} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.7882 (0.1995) & 0.5507 (0.0685)  \\ \hline
OS & 0.5322 (0.3393) & 0.9608 (0.2427) \\ \hline
\end{tabular}
\label{tab:OSY} 
\end{table}
\begin{figure}[H]
  \caption{OSY Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{OSY_QM.png}  
  \label{fig:OSY_QM}
\end{figure}
\newpage
\subsection{TNK} 
This test problem, denoted as TNK in \cite{deb2001multi} is shown below with the true Pareto frontier shown in Figure~\ref{fig:TNK_true}. Constraint parameters CF1 and CF2 were both chosen to be 0.01 to place equal emphasis on amount of infeasibility and number of violated constraints.

@@

\noindent Figure~\ref{fig:TNK} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:TNK} summarizes the mean quality metrics for each algorithm for ten runs.
\begin{figure}[h]
  \caption{Example Pareto Results for TNK}
  \centering
  \includegraphics[width=0.85\textwidth]{TNK_pareto_final.png}  
  \label{fig:TNK}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for TNK} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD &  0.8581 (0.0480) & 0.7792 (0.0036) \\ \hline
OS & 0.4177 (0.3216) & 0.9763 (0.0178)\\ \hline
\end{tabular}
\label{tab:TNK} 
\end{table}
\begin{figure}[H]
  \caption{TNK Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{TNK_QM.png}  
  \label{fig:TNK_QM}
\end{figure}

@@

\noindent Figure~\ref{fig:CTP} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:CTP} summarizes the mean quality metrics for each algorithm for ten runs \cite{deb2001multi}.
\begin{figure}[h]
  \caption{Example Pareto Results for CTP}
  \centering
  \includegraphics[width=0.85\textwidth]{CTP_pareto_final.png}  
  \label{fig:CTP}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for CTP} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.6802 (0.0067) &  0.6802 (0.0092) \\ \hline
OS & 0.7901 (0.0734) & 0.5959 (0.1324) \\ \hline
\end{tabular}
\label{tab:CTP} 
\end{table} 
\begin{figure}[H]
  \caption{CTP Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{CTP_QM.png}  
  \label{fig:CTP_QM}
\end{figure}

\noindent The mean values for coverage difference are exactly the same for both algorithms. In fact a paired t-test also shows the means are not statistically difference(p>0.05). For Pareto spread, MATLAB's MOGA performs the highest.
\newpage
\section{Robust Problems} 
To solve problems with an uncertain variable we implement RMOGA.  One way to ensure robustness for a given population considered in GA, is by finding the value of the uncertain variable which maximizes the constraint values acording to each member in the population.  Another way is to discretize the dependent variable and then find which uncertain variable in this set maximizes the constraint values.  This latter method is the one we chose because of the decreased execution time over the former.  These two options are shown in figure \ref{fig:discretize}.
   Since the uncertainty term only appears in the constraints portion of both of the problems we consider this discretization is fairly simple.  In addition, since the uncertain terms are linearly combined in the constraints, this discretization is trivial.

@@

\noindent Figure~\ref{fig:robust} shows a sample result from both MATLABs built in MOGA and the robust MOGA developed in this project. Table~\ref{tab:robustTNK} summarizes the mean quality metrics for each algorithm for ten runs. \newline
\begin{figure}[H]
  \caption{Example Pareto Results for TNK}
  \centering
  \includegraphics[width=0.85\textwidth]{prob7_nChr25_nRun400.png}  
  \label{fig:robustTNK}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for Robust TNK (10 Runs)} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric &  Our MOGA \\ \hline
CD & 0.95 (0.014) \\ \hline
OS & 0.66 (0.012) \\ \hline
\end{tabular}
\label{tab:robustTNK} 
\end{table}

\noindent Comparing the estimated Pareto frontiers to the true Pareto frontier, is is clear that our MOGA outperforms MATLAB's MOGA. The Pareto spread in our MOGA is significantly higher however the coverage difference is higher in MATLABs MOGA (p<0.05).

\subsection{Flight Planning Problem (FPP)}
Now let us consider the final problem where we try to minimize the total flight time from the start location $(0,12.5)$ to the finish location $(40,12.5)$.  In this problem there is a know wind velocity field which changes the total velocity of the aircraft with respect to the ground.  At the same time, we want to maximize the distance of the flight path from some group of some exclusion zones. This also introduces a constraint that requires the flight path not intersect the exclusion zone. Each exclusion zone is approximated by a circle with known centers.  The radius of each exclusion zone is known to $\pm 2m$.  As a result this problem can be approached as a bi-objective optimization with a robust feasibility constraint.

@@

\noindent The function $flightTime(\textbf{x},\textbf{y})$ is a black-box. The values $\textbf{xc}_j$ and  $\textbf{yc}_j$ specify the exclusion zone centers while $\textbf{r}_j$ specify the radii. A solution to this problem is shown in figure \ref{fig:FPP}.  In this figure there are two exclusion zones.
\begin{figure}[H]
  \caption{True Pareto Frontier for CTP}
  \centering
  \includegraphics[width=0.85\textwidth]{FPP.png}  
  \label{fig:FPP}
\end{figure}

\begin{figure}[H]
  \caption{True Pareto Frontier for CTP}
  \centering
  \includegraphics[width=0.85\textwidth]{FPP_pareto.png}  
  \label{fig:FPP_pareto}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for Robust FPP (10 Runs)} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric &  Our MOGA \\ \hline
CD & 0.2427 (0.0704) \\ \hline
OS & 0.4794 (0.1220) \\ \hline
\end{tabular}
\label{tab:robustTNK} 
\end{table}

@@

Overall, it was found that different optimization algorithms result in a range of solutions for a given test problem. Thus it is important, when developing an optimization algorithm, to test against a range of optimization problems. In addition, it was also concluded that special attention should be paid to tunable parameters within each algorithm. Understanding the nature of the parameter and how it affects the algorithm is crucial to obtaining the "true" Pareto frontier.

>>>>

This report develops multi-objective optimization methods using genetic algorithms. Three cases of multi-objective optimization are considered: unconstrained optimization, constrained optimization, and robust optimization. A fitness function for the first two cases was developed using the built-in MATLAB 'ga' routine. The last case was developed such that uncertainty in function parameters could be handled and robustly optimized against.\newline

\noindent For the first two methods, each method developed was evaluated through the use of well-known test problems. The resulting Pareto frontier of each method was evaulated in terms of quality metrics. Finally, the results of the developed methods were compared to results obtained by using the built-in MATLAB 'gamultiobj' routine for the unconstrained and constrained cases.  In the first robust problem, we compare the results against the non-robust MOGA.  In the second robust problem there is not an objective comparison.

@@

\noindent The true Pareto frontier for this problem occurs when $x_i = 0$ for i = 2,...,30. Figure~\ref{fig:ZDT1} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. In this problem, $\alpha=1$, $\sigma = 0.158$, and $\epsilon = 0.22$. The final results were found using 300 chromosomes in each population. The quality metrics chosen to evaluate this problem (and all other problems) are Coverage Difference (CD) and Overall Pareto Spread (OS). Ten runs for each algorithm were performed using the same initialization parameters and the mean and standard deviation of each metric are tabulated in Table~\ref{tab:ZDT1}.

\begin{figure}[H]
  \caption{Example Pareto Results for ZDT1}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT1_pareto_final.png}  
  \label{fig:ZDT1}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for ZDT1} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.3874 (0.0164) &  0.3582 (0.0040) \\ \hline
OS & 0.9605 (0.1088) & 0.9283 (0.0928) \\ \hline
\end{tabular}
\label{tab:ZDT1} 
\end{table}
\begin{figure}[H]
  \caption{ZDT1 Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT1_QM.png}  
  \label{fig:ZDT1_QM}
\end{figure}

@@

\begin{table}[H]
\caption{Quality Metrics for ZDT2} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline 
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.7832  (0.0821) & 0.6971  (0.0094) \\ \hline
OS &  0.8781 (0.0946) & 1.0086 (0.0278)  \\ \hline
\end{tabular}
\label{tab:ZDT2} 
\end{table}
\begin{figure}[H]
  \caption{ZDT2 Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT2_QM.png}  
  \label{fig:ZDT2_QM}
\end{figure}

\subsection{ZDT3} 
The third test problem, denoted as ZDT3 in \cite{deb2001multi} is shown below.

@@

\noindent The true Pareto frontier for this problem again occurs when $x_i$ = 0 for i = 2,...,30. The fitness parameters selected in this problem were $\alpha = 1$, $\sigma = 0158$ and $\epsilon = 0.22$. Again, the number of chromosomes in this problem was 300. Figure~\ref{fig:ZDT3} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:ZDT3} summarizes the mean quality metrics for each algorithm for ten runs. \newline

@@

\begin{table}[H]
\caption{Quality Metrics for ZDT3} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline 
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.7407 (0.0050) & 0.7554 (0.0031) \\ \hline
OS & 0.8565 (0.0098) & 0.8489 (0.0180) \\ \hline
\end{tabular}
\label{tab:ZDT3} 
\end{table}
\begin{figure}[H]
  \caption{ZDT3 Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{ZDT3_QM.png}  
  \label{fig:ZDT3_QM}
\end{figure}

@@

\noindent Figure~\ref{fig:OSY} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:OSY} summarizes the mean quality metrics for each algorithm for ten runs.
\begin{figure}[H]
  \caption{Example Pareto Results for OSY}
  \centering
  \includegraphics[width=0.85\textwidth]{OSY_pareto_final.png}  
  \label{fig:OSY}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for OSY} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.7882 (0.1995) & 0.5507 (0.0685)  \\ \hline
OS & 0.5322 (0.3393) & 0.9608 (0.2427) \\ \hline
\end{tabular}
\label{tab:OSY} 
\end{table}
\begin{figure}[H]
  \caption{OSY Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{OSY_QM.png}  
  \label{fig:OSY_QM}
\end{figure}
\newpage
\subsection{TNK} 
This test problem, denoted as TNK in \cite{deb2001multi} is shown below with the true Pareto frontier shown in Figure~\ref{fig:TNK_true}. Constraint parameters CF1 and CF2 were both chosen to be 0.01 to place equal emphasis on amount of infeasibility and number of violated constraints.

@@

\noindent Figure~\ref{fig:TNK} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:TNK} summarizes the mean quality metrics for each algorithm for ten runs.
\begin{figure}[H]
  \caption{Example Pareto Results for TNK}
  \centering
  \includegraphics[width=0.85\textwidth]{TNK_pareto_final.png}  
  \label{fig:TNK}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for TNK} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD &  0.8581 (0.0480) & 0.7792 (0.0036) \\ \hline
OS & 0.4177 (0.3216) & 0.9763 (0.0178)\\ \hline
\end{tabular}
\label{tab:TNK} 
\end{table}
\begin{figure}[H]
  \caption{TNK Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{TNK_QM.png}  
  \label{fig:TNK_QM}
\end{figure}

@@

\noindent Figure~\ref{fig:CTP} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:CTP} summarizes the mean quality metrics for each algorithm for ten runs \cite{deb2001multi}.
\begin{figure}[H]
  \caption{Example Pareto Results for CTP}
  \centering
  \includegraphics[width=0.85\textwidth]{CTP_pareto_final.png}  
  \label{fig:CTP}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for CTP} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.6802 (0.0067) &  0.6802 (0.0092) \\ \hline
OS & 0.7901 (0.0734) & 0.5959 (0.1324) \\ \hline
\end{tabular}
\label{tab:CTP} 
\end{table} 
\begin{figure}[H]
  \caption{CTP Quality Metrics}
  \centering
  \includegraphics[width=0.85\textwidth]{CTP_QM.png}  
  \label{fig:CTP_QM}
\end{figure}

\noindent The mean values for coverage difference are exactly the same for both algorithms. In fact a paired t-test also shows the means are not statistically difference(p>0.05). For Pareto spread, MATLAB's MOGA performs the highest.
\newpage
\section{Robust Problems} 
To solve problems with an uncertain variable we implement RMOGA. There are different approaches for implementing robust constraints in MOGA \cite{hu2009improving}\cite{li2006new}. One way to ensure robustness for a given population considered in GA, is by finding the value of the uncertain variable which maximizes the constraint values according to each member in the population .  Another way is to discretize the dependent variable and then find which uncertain variable in this set maximizes the constraint values.  This latter method is the one we chose because of the decreased execution time over the former.  These two options are shown in figure \ref{fig:discretize}.
   Since the uncertainty term only appears in the constraints portion of both of the problems we consider this discretization is fairly simple.  In addition, since the uncertain terms are linearly combined in the constraints.

@@

\noindent Figure~\ref{fig:robustTNK} shows a sample result from both MATLABs built in MOGA and the robust MOGA developed in this project. Table~\ref{tab:robustTNK} summarizes the mean quality metrics for each algorithm for ten runs. \newline
\begin{figure}[H]
  \caption{Example Pareto Results for TNK}
  \centering
  \includegraphics[width=0.85\textwidth]{prob7_nChr25_nRun400.png}  
  \label{fig:robustTNK}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for Robust TNK (10 Runs)} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline 
Metric &  Our MOGA \\ \hline
CD & 0.95 (0.014) \\ \hline
OS & 0.66 (0.012) \\ \hline
\end{tabular}
\label{tab:robustTNK} 
\end{table}

\noindent Comparing the estimated Pareto frontiers to the true Pareto frontier, is is clear that our MOGA outperforms MATLAB's MOGA. The Pareto spread in our MOGA is significantly higher however the coverage difference is higher in MATLABs MOGA ($p<0.05$ ).

\subsection{Flight Planning Problem (FPP)}
Now let us consider the final problem where we try to minimize the total flight time from the start location $(0,12.5)$ to the finish location $(40,12.5)$.  In this problem there is a known wind velocity field which changes the total velocity of the aircraft with respect to the ground.  At the same time, we want to maximize the distance of the flight path from the centers of a group of exclusion zones. This also introduces a constraint that requires the flight path not intersect the exclusion zone. Each exclusion zone is approximated by a circle with known centers.  The radius of each exclusion zone is known to $\pm 2m$.  As a result this problem can be approached as a bi-objective optimization with a robust feasibility constraint.

@@

\noindent The function $flightTime(\textbf{x},\textbf{y})$ is a black-box. The values $\textbf{xc}_j$ and  $\textbf{yc}_j$ specify the exclusion zone centers while $\textbf{r}_j$ specify the radii. A solution to this problem is shown in figure \ref{fig:FPP}.  In this figure there are two exclusion zones marked in blue. Since this is a bi-objective function, there are multiple optimal solutions.  These solutions are form a Pareto Frontier.  The distances to the closest exclusion zone center are negative because this is a maximization problem.
\begin{figure}[H]
  \caption{Flight Path with exclusion zones. The exclusion zones are marked in blue.  The dotted blue line indicates the robust boundary.}
  \centering
  \includegraphics[width=0.85\textwidth]{FPP.png}  
  \label{fig:FPP}
\end{figure}

\begin{figure}[H]
  \caption{True Pareto Frontier for CTP}
  \centering
  \includegraphics[width=0.85\textwidth]{FPP_pareto_units.png}  
  \label{fig:FPP_pareto}
\end{figure}

\begin{table}[H]
\caption{Quality Metrics for Robust FPP (10 Runs)} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline  
Metric &  Our MOGA \\ \hline
CD & 0.2427 (0.0704) \\ \hline
OS & 0.4794 (0.1220) \\ \hline
\end{tabular}
\label{tab:robustFPP} 
\end{table}

We chose to approach the robust FPP using a constraint which maximizes the distance of the \bf closest \rm point in the trajectory to the exclusion zone.  If we try to maximize the distance of all of the points, then the optimization will take advantage of the way that the flight path is approximated by the waypoints;  all of the waypoints will be stacked in the corner farthest from the exclusion zone and there is a risk that the fitted path will pass through the exclusion zone.  Maximizing the closest point side-steps this problem.

Another interesting thing about this problem is when there are two exclusion zones, it is easy to see that the Pareto frontier maximizing  the distance approaches the midpoint between the two exclusion zones. This phenomena is visible in figure \ref{fig:FPP_pareto} where the midpoint is at $12.5$ m from the exclusion zone and the Pareto Frontier approaches it.

@@

Overall, it was found that different optimization algorithms result in a range of solutions for a given test problem. Thus it is important, when developing an optimization algorithm, to test against a range of optimization problems. In addition, it was also concluded that special attention should be paid to tunable parameters within each algorithm. Understanding the nature of the parameter and how it affects the algorithm is crucial to obtaining the "true" Pareto frontier. In addition, we were impressed with GA's ability to find many different minima; the presence of multiple minima would be a problem for a gradient based solver. Of course the increased time to a solution with no guarantee of optimality is the trade-off when using sampling algorithm.
